Continuous Generalization of Buildings \\ by Growing and Aggregating

### 2017-09-12 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
polished section of aggregating close buildings by introducing bridges

Our aggregation is based on growing and some of simplifying. 
So we present the two operators before aggregating.

\subsection{Growing buildings based on buffering}
\label{sec:Grow}
We grow building based on buffering. 
There are two typical ways of buffering a polygon, i.e.,
one with round joins and the other with miter joins 
(see \fig\ref{fig:Buffer_TwoKinds}).
As buildings are usually rectangles, 
we choose the second way to
better preserve the right angles.
If an angle is acute, however, an excessively long \emph{spike} will be 
produced.
This spike may go across other buildings 
(see \fig\ref{fig:Buffer_MiterLimits}a).
To avoid this kind of interruptions, 
we require that if a vertex of the 
buffer is more than $\alpha \dtrm{G} (\alpha \ge 1)$
away from the original vertex, 
a \emph{square} join is applied
(see \fig\ref{fig:Buffer_MiterLimits}b).
Distance $\dtrm{G}$ is the growth at time $t$.
We denote by $d_\mathrm{G}$ the growth for goal map.
Then we define
\begin{equation}
\label{eq:d_Gt}
\dtrm{G} = t \cdot d_\mathrm{G}.
\end{equation}
To keep right angles of buildings, 
we must have $\alpha \geq \sqrt{2}$. 
We set $\alpha  = 1.5$ so that a square join is applied when an angle is 
smaller (more acute) than $83.6 \degree$.

@@

@@

We wish to remove ``bays'' 
which have ``widths'' less than $r_\mathrm{h} = 2\sqrt{a_\mathrm{h}/\pi}$.
Variable $a_\mathrm{h}$ is the least area for a hole to be presented on map.
Following \citep{Chaudhry2008}, we set $a_\mathrm{h} = 8\,\mathrm{mm}^2$.
Variable $r_\mathrm{h}$ is the radius of such a hole 
supposing that the hole is a circle.
Sometimes, our $\dtrm{D}$ is not large enough to do so 
because of the limitation from \eq\ref{eq:d_Dt}.
We define
\[
\dtrm{D} =\min (\frac{\dtrm{G}-\dtrm{E}}{\alpha - 1}, r_\mathrm{h} M_t) .
\]

After carrying out the buffering-based methods, 
we simplify the grown buildings using Imai--Iri algorithm 
\citep{ImaiIri1988}.
This algorithm first finds all the valid shortcuts of a polyline.
A shortcut is valid for a segment 
if the distance between the segment and the shortcut is at most a specified 
value
(see \fig\ref{fig:ImaiIri_Shortcut}).
We set the value also as $l$.
That is, at time $t$, the threshold distance is
\begin{equation}
\label{eq:d_lt}
d_{l,t}= l \cdot M_t.
\end{equation}
Second, the algorithm finds a sequence of valid shortcuts, from the beginning 
of a polyline to the end, using breadth-first search.
The sequence of valid shortcuts is an approximation of the polyline, 
and has the least number of line segments.

@@

\todo[inline]{more details in the below paragraph?}
We add two more constraints for a shortcut to be valid. 
First, a shortcut must be completely inside the grown building.
If a shortcut is outside,
we are not able to arrive at the shortcut by growing.
Second, a shortcut is not allowed to intersect the 
boundary of the original building.
If we allow this intersection, 
we need to shrink the building instead of growing. 
Of course, we do not want to shrink.

@@

\subsection{Grouping buildings based on buffering}
\label{sec:Group}
%There are many ways to group buildings.
%
%Using MST to group buildings: \citet{Zhang2013, 
%	Cetinkaya2015,Deng2017,Regnauld1996}

Original buildings grow according to time $t$.
We put the original building in the same group if 
they grow to become too close.
We group buildings based on buffering.
(see \fig\ref{fig:RemoveBay} for example).
We wish to remove some ``bays'' 
which have widths less than $2 \dtrm{D}$.
A bay may appear after some buildings are merged by bridging
(see for example \fig\ref{fig:RemoveBay}e).
To remove such kind of bay,
we overgrow (see \fig\ref{fig:RemoveBay}b and~e) 
and then erode back (see \fig\ref{fig:RemoveBay}c and~f) 
with distance $\dtrm{D}$.
There may be some buildings in a bay (see \fig\ref{fig:RemoveBay}c),
so we iteratively group until the number of groups does not decrease.
The result of having removed a bay is the outer polygon of 
\fig\ref{fig:RemoveBay}h. 
In comparison, the result is \fig\ref{fig:RemoveBay}e 
if we do not remove a bay.
Note that the pit we want to remove in \fig\ref{fig:RemovePitAndSpike} is a 
kind of bay and will be removed by overgrowing.

@@

\subsection{Aggregating close buildings by introducing bridges}
\label{sec:Merge}
The distance between two buildings on a map should be larger than a threshold
\citep{Regnauld2001,Li2004}.
Following \citet{Basaraner2008,Stoter2009}, 
we set the separation threshold $\epsilon= 0.2\,\mathrm{mm}$. 
The real separation distance at time $t$ is
\begin{equation}
	\label{eq:d_epsilont}
	d_{\epsilon, t} = \epsilon \cdot M_t.
\end{equation}

If a group of buildings become too close during growing,
we merge them by introducing bridges (see \fig\ref{fig:GrowAndBridge}).
We will talk about where to add bridges in \sect\ref{sec:Goal}.
No matter a bridge appear earlier or later, 
it has width $2\dtrm{G}$ at time $t$.
This setting guarantees that no bridge is thin when $t=1$.
For example, the two bridges in \fig\ref{fig:GrowAndBridge} at time $t=1$ have 
the same widths.
This setting is achieved by following.
We detect nearest points for each pair of buildings at time $t=0$ so that 
we know where we should add bridges.
At time $t$, we group buildings that are too close to each other,
then we merge them by adding the precomputed bridges.
For this merged building, we grow, simplify, and unite as described in 
\sects\ref{sec:Grow}, \ref{sec:Simplify}, and~\ref{sec:Unite}.
We may unite the processed merged building with several separate parts 
because the group of buildings may be in several smaller groups
in the immediately previous step.

\todo[inline]{actually larger than $d_{\epsilon, t}$.}

\begin{figure*}[tb]
	\centering
	\includegraphics[draft=false]{GrowAndBridge}
	\caption{Merge buildings by introducing bridges when the buildings become 
		too close.
		Although the bridges appear at different time, 
		their widths are the same (see the figure with $t=1$).}
	\label{fig:GrowAndBridge}
\end{figure*}

For each pair of buildings in the same group, 
we find the smallest distance between them.
We connect the buildings by adding an edge from the nearest points.
We find a minimum spanning tree of the buildings using Prim's algorithm 
\citep{Prim1957}.
We enlarge and merge buildings as the way we do in \sect\ref{sec:Group}.

@@

@@

\begin{figure*}[tb]
	\centering
	\includegraphics{Data}
	\caption{scale.}
	\label{fig:Data}
\end{figure*}

>>>>

Our grouping is based on growing, aggregating and some of simplifying. 
So we present the three operators before grouping.

\subsection{Growing buildings based on buffering}
\label{sec:Grow}
We grow buildings based on buffering. 
There are two typical ways of buffering a polygon, i.e.,
one with round joins and the other with miter joins 
(see \fig\ref{fig:Buffer_TwoKinds}).
As buildings are usually rectangles, 
we choose the second way to
better preserve the right angles.
If an angle is acute, however, an excessively long \emph{spike} will be 
produced.
This spike may go across other buildings 
(see \fig\ref{fig:Buffer_MiterLimits}a).
To avoid this kind of interruptions, 
we require that if a vertex of the 
buffer is more than $\alpha \dtrm{G} (\alpha \ge 1)$
away from the original vertex, 
a \emph{square} join is applied
(see \fig\ref{fig:Buffer_MiterLimits}b).
Distance $\dtrm{G}$ is the growth at time $t$.
We denote by $d_\mathrm{G}$ the growth for goal map.
Then we define
\begin{equation}
\label{eq:d_Gt}
\dtrm{G} = t \cdot d_\mathrm{G}.
\end{equation}
To keep right angles of buildings, 
we must have $\alpha \geq \sqrt{2}$. 
We set $\alpha  = 1.5$ so that a square join is applied when an angle is 
smaller (more acute) than $83.6 \degree$.

@@

\subsection{Aggregating close buildings by introducing bridges}
\label{sec:Merge}

If a group of buildings will become too close at time $t$ because of growing,
we aggregate the original buildings by introducing bridges, 
then we grow the bridged building (see \fig\ref{fig:GrowAndBridge}).
We show how to group buildings for time $t$ in \sect\ref{sec:Group}.
No matter a bridge appears earlier or later, 
it has width $2\dtrm{G}$ at time $t$.
This setting guarantees that no bridge is thin when $t=1$.

\begin{figure*}[tb]
	\centering
	\includegraphics[draft=false]{GrowAndBridge}
	\caption{Aggregate original buildings in the same group by introducing 
	bridges.
		Then grow the bridged buildings.}
	\label{fig:GrowAndBridge}
\end{figure*}

For each pair of buildings in the same group, 
we find a nearest pair of points.
We connect the buildings by adding a line segment bridging the nearest points.
If we consider each building as a node and each line segment as an edge, 
then we have a graph.
Using Prim's algorithm \citep{Prim1957}, 
we find a minimum spanning tree (MST) in the graph
taking the lengths of the line segments as the weights.
As a results, the line segments corresponding to the edges in the MST
are used as bridges to aggregate the buildings.

@@

We wish to remove ``bays'' 
which have ``widths'' less than $2 r_\mathrm{h}$. 
Variable $r_\mathrm{h}= 2\sqrt{a_\mathrm{h}/\pi}$
is the radius of a hole which is just large enough to be presented on map.
Following \citep{Chaudhry2008}, we set area $a_\mathrm{h} = 8\,\mathrm{mm}^2$.
Sometimes, our $\dtrm{D}$ is not large enough to do so 
because of the limitation from \eq\ref{eq:d_Dt}.
We define
\[
\dtrm{D} =\min (\frac{\dtrm{G}-\dtrm{E}}{\alpha - 1}, r_\mathrm{h} M_t) .
\]

After carrying out the dilation-erosion-dilation-based method, 
we simplify the buildings using Imai--Iri algorithm 
\citep{ImaiIri1988}.
First, this algorithm finds all the valid shortcuts of a polyline.
A shortcut is valid for a segment 
if the distance between the segment and the shortcut is at most a specified 
value
(see \fig\ref{fig:ImaiIri_Shortcut}).
We set the value also as $l$.
That is, at time $t$, the threshold distance is
\begin{equation}
\label{eq:d_lt}
d_{l,t}= l \cdot M_t.
\end{equation}
Second, the algorithm finds a sequence of valid shortcuts, from the beginning 
of a polyline to the end, using breadth-first search.
The sequence of valid shortcuts is an approximation of the polyline 
and has the least number of line segments, with error smaller than $d_{l,t}$.

@@

We add two more constraints for a shortcut to be valid. 
First, a shortcut must be completely inside the grown building.
If a shortcut is outside,
we are not able to arrive at the shortcut by growing.
Second, a shortcut is not allowed to intersect with the aggregated building.
If we allow this intersection, 
the building will have to be shrunk. 
Of course, we do not want to shrink.
\todo{a shortcut is not allowed to intersect with the building at the 
immediately previous step?}

@@

\subsection{Grouping buildings based on buffering}
\label{sec:Group}
There are many research works about grouping buildings.
\citet{Cetinkaya2015} and \citet{Deng2017} compared some of the methods.
However, our two needs, 
the distances between buildings are always larger than a specified threshold 
and small bays should be removed, 
motivate us to develop our own grouping method.

Original buildings grow according to time $t$.
We put the original buildings in the same group if 
they grow to become too close.
We group buildings based on buffering.
The basic idea is that 
we buffer the original buildings with distance $\dtrm{G}$
and an additional distance $\dtrm{C}$.
If two buffers overlap, 
then the original buildings are put in the same group.

%(see \fig\ref{fig:RemoveBay} for example).
As stated in \sect\ref{sec:Simplify}, 
we wish to remove ``bays'' 
which have widths less than $2 \dtrm{D}$.
A bay may come from a complex original building,
or from bridging some buildings.
\fig\ref{fig:RemoveBay}e shows an example of the latter case.
To remove a bay,
we overgrow (see \fig\ref{fig:RemoveBay}b and~e) 
and then erode back (see \fig\ref{fig:RemoveBay}c and~f) 
with distance $\dtrm{D}$.
There may be some buildings in a bay (see \fig\ref{fig:RemoveBay}c),
so we iteratively group until the number of groups does not decrease.
For the buildings in \fig\ref{fig:RemoveBay}a,
the final result of removing a bay is the outer polygon of 
\fig\ref{fig:RemoveBay}h. 
In comparison, the result is \fig\ref{fig:RemoveBay}e 
if we do not dilate (setting $\dtrm{D}=0$) to remove a bay.
Note that the pit we want to remove in \fig\ref{fig:RemovePitAndSpike} is a 
kind of bay and will be removed by overgrowing.

@@

Definition of $\dtrm{C}$

The distance between two buildings on a map should be larger than a threshold.
Following \citet{Stoter2009}, 
we set the separation threshold $\epsilon= 0.2\,\mathrm{mm}$. 
The real separation distance at time $t$ is
\begin{equation}
\label{eq:d_epsilont}
d_{\epsilon, t} = \epsilon \cdot M_t.
\end{equation}

@@

We may unite the processed merged building with several separate parts 
because the group of buildings may be in several smaller groups
in the immediately previous step.

@@

\begin{figure*}[tb]
	\centering
	\includegraphics{Data}
	\caption{data.}
	\label{fig:Data}
\end{figure*}
